The Astropy Project

### 2017-12-10 main.tex
fix typo

\acknowledgments The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors. We also
thank NumFOCUS and the Python Software Foundation for financial
support. Within the academic community, we thank
institutions that make it possible that astronomers and other developers on
their staff can contribute their time to the development of
\astropy projects.

Furthermore, the \astropy packages would not exist
in their current form without a number of web services for code
hosting, continuous integration, and documentation; in particular,
\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
Read the Docs.

\astropypkg interfaces with the SIMBAD database,
operated at CDS, Strasbourg, France. It also makes use of the ERFA library \citep{erfa},
which in turn derives from the IAU SOFA Collection\footnote{http://www.iausofa.org} developed by the International Astronomical Union Standards of Fundamental Astronomy \citep{sofa}.

\software{\package{astropy} (\citealt{astropy}),
          \package{numpy} (\citealt{numpy}),
          \package{scipy} (\citealt{scipy}),
          \package{matplotlib} (\citealt{matplotlib}),
          \package{Cython} (\citealt{cython}),
          \package{SOFA} (\citealt{sofa}),
          \package{ERFA} (\citealt{erfa})
          }

>>>>

\acknowledgments

Who to thank?  numfocus, GSOC, Python Software Foundation

We thank the many web services that make developing and maintaining this package
feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.

\software{\package{astropy} (\citealt{astropy}),
          \package{numpy} (\citealt{numpy}),
          \package{scipy} (\citealt{scipy}),
          \package{matplotlib} (\citealt{matplotlib}),
          \package{Cython} (\citealt{cython}),
          }
